\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-03-27 chapters/3_algorithm.tex
Improve formatting

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
\caption{\small 
Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph...  
\label{fig:edge_contraction_and_contr_graph} }
\end{figure}

@@

\begin{algorithm}
  \caption{Unified Graph Agglomerative Clustering}
   \hspace*{\algorithmicindent} \textbf{Inputs:} graph $\mathcal{G}(V,E,W)$; bool {\color{blue}\texttt{addCannotLink}}  \\
  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering and contracted graph $\mathcal{G}'$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]

@@

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.png}
\caption{\small 
Example of agglomerative clustering on signed graph with and without cannot-link constraints...
\label{fig:algorithm_with_without_CLC}}
\end{figure}

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{r l || c | c | c}
            % \toprule\toprule
             & &  \multirow{3}{*}{\textbf{Unsigned graphs}}  & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            & & &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\

            & & &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
            % \cmidrule[0.3em]{3-5}
            % \midrule[0.15em]
            \midrule\midrule
            Sum: & $f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$ & \thead{Sum Linkage\\Hierarchical Clustering} & \thead{Greedy Additive \\ Edge Contraction \cite{levinkov2017comparative}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ \midrule

            \makecell[r]{Absolute \\ maximum:} & \makecell[l]{$f(\tilde{w}_1,\tilde{w}_2) =\argmax_{\tilde{w}\in\{\tilde{w}_{1},\tilde{w}_{2}\}} \big|\tilde{w} \big| $}   & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Mutex Watershed \cite{wolf2018mutex}} \\ \midrule

            \makecell[r]{Arithmetic \\mean:} & $f(\tilde{w}_1,\tilde{w}_2) = \mathrm{weightedAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $                                 & \thead{ Average Linkage\\ Hierarchical Clustering \\(UPGMA) \cite{lance1967general}} & \thead{Signed Agglomerative Clust. \\ with Average Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Maximum: & $f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Single Linkage\\Hierarchical Clustering\\ \cite{lance1967general}} & \thead{Signed Agglomerative Clust. \\ with Single Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Minimum:& $f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $                                 & \thead{Complete Linkage\\ Hierarchical Clustering \\ \cite{lance1967general}}  & \thead{Signed Agglomerative Clust. \\ with Complete Linkage \\ (\textbf{NEW})} & \thead{\textbf{NEW}}

>>>>

\begin{minipage}[b]{\textwidth}
        \centering
        \begin{minipage}[b]{0.45\textwidth}
\centering
        \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
\captionof{figure}{\small 
Example of edge contraction: the edge $e_{uv}$ is selected from priority queue; after nodes $u$ and $v$ are merged and $e_{uv}$ is deleted, there are two double edges $e_1$ and $e_2$ left in the graph...  
\label{fig:edge_contraction_and_contr_graph} }
    \end{minipage}\hspace{0.04\textwidth}
    \begin{minipage}[b]{0.45\textwidth}
        \centering
\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.png}
\captionof{figure}{\small 
Example of agglomerative clustering on signed graph with and without cannot-link constraints...
\label{fig:algorithm_with_without_CLC}}
    \end{minipage}
\end{minipage}

@@

\begin{algorithm}
  \caption{Unified Graph Agglomerative Clustering \TODO{adapt to width}}
   \hspace*{\algorithmicindent} \textbf{Inputs:} graph $\mathcal{G}(V,E,W)$; bool {\color{blue}\texttt{addCannotLink}}  \\
  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering and contracted graph $\mathcal{G}'$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]

@@

\begin{table*}
    \centering
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{r l || c | c | c}
            % \toprule\toprule
             & &  \multirow{3}{*}{\textbf{Unsigned graphs}}  & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            & & &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\

            & & &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
            % \cmidrule[0.3em]{3-5}
            % \midrule[0.15em]
            \midrule\midrule
            Sum: & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$} & \thead{Sum Linkage\\Hierarchical Clust.} & \thead{Greedy Additive \\ Edge Contraction \\\cite{levinkov2017comparative}} & \thead{Greedy \\Fixation \\\cite{levinkov2017comparative}} \\ \midrule

            \makecell[r]{Abs. \\ max:} & \thead[l]{
            $
            f(\tilde{w}_1,\tilde{w}_2) = \begin{cases} 
            \tilde{w}_1 & \text{if}\,\, |\tilde{w}_1|>|\tilde{w}_2|\\
            \tilde{w}_2 & \text{otherwise}
             \end{cases} 
            $}
               & \thead{Single Linkage\\Hierarchical Clust.\\ \cite{lance1967general}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} \\ \midrule
            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \mathrm{wAvg}\{ \tilde{w}_1, \tilde{w}_2 \} $}                                 & \thead{ Average Linkage\\ Hierarchical Clust. \\(UPGMA) \cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl. Clust. \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Max: & \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \max \{ \tilde{w}_1, \tilde{w}_2 \}  $}                                 & \thead{Single Linkage\\Hierarchical Clust.\\ \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl. Clust. \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Min:& \thead[l]{$f(\tilde{w}_1,\tilde{w}_2) = \min \{ \tilde{w}_1, \tilde{w}_2 \}  $}                                 & \thead{Complete Linkage\\ Hierarchical Clust. \\ \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl. Clust. \\ (\textbf{NEW})} & \thead{\textbf{NEW}}

### 2019-03-27 chapters/5_experiments_cityscapes.tex
Improve formatting

% !TEX root = ../agglo_clust_review.tex
\subsection{Results on Cityscapes}
In the experiments on the cityscapes dataset, we used the pipeline proposed by \cite{liu2018affinity} \UPDATE{that currently represents the method not using any external dataset like MS-COCO}...
\begin{table}
    \centering
    \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
        \toprule
        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.343}  & 0.339  \\
GMIS \cite{liu2018affinity} & 0.341 & -  \\
Max &   0.243  &   0.325  \\
Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
Min &  0.000    & 0.000  \\
        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{AP scores on the cityscapes validation set for UGACA and different types of update rules. \TODO{PROBLEM: all apart from GMIS uses finetuned affinities} }
    \label{tab:results_cityscapes}
\end{table}

>>>>

% !TEX root = ../agglo_clust_review.tex
\subsection{Results on Cityscapes}
In the experiments on the cityscapes dataset, we used the pipeline proposed by \cite{liu2018affinity} \UPDATE{that currently represents the method not using any external dataset like MS-COCO}...

### 2019-03-27 chapters/5_experiments_noise.tex
Improve formatting

% !TEX root = ../agglo_clust_review.tex
% 
\begin{figure}
\centering

        \includegraphics[width=0.48\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}

    \caption{The two figures represent the predictions of the CNN on the CREMI dataset (\UPDATE{REF}) a) without added noise, b) with the addition of the merge-biased noise defined in Eq. \ref{eq:opensimplex_noise_def} and c) with split-biased noise. The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries \TODO{Add colorbar? Adapt to noise defs}}
    \label{fig:noisy_affs}
\end{figure}%

\begin{figure*}
\centering
        \begin{subfigure}[t]{0.48 \textwidth}
        \centering
        \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}

@@

\caption{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights... Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.    \TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
\end{figure*}

@@

>>>>

% !TEX root = ../agglo_clust_review.tex
%

\begin{figure}
\centering
        \begin{subfigure}[t]{0.48 \textwidth}
        \centering
        \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}

@@

\caption{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights... Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.    \TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
\end{figure}

% \begin{minipage}[b]{0.48\textwidth}
% % \begin{figure}
%         % \begin{subfigure}[t]{0.48 \textwidth}
%         \centering
%         \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}

%         \captionof{subfigure}{Merge-biased opensimplex noise} \label{fig:thresh}
%     \end{minipage}\hfil
% \begin{minipage}[b]{0.48\textwidth}
%     % \end{subfigure}%
%     % \begin{subfigure}[t]{0.48 \textwidth}
%         \centering
%         \includegraphics[width=0.98\textwidth,trim=0.29in 0.31in 0.31in 0.31in,clip]{./figs/split_noise.pdf}
%         \captionof{subfigure}{Split-biased opensimplex noise} \label{fig:ws}
%     % \end{subfigure}
% \captionof{figure}{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights... Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.    \TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
% % \end{figure}

@@

\begin{minipage}[T!]{\textwidth}
        \centering
        \begin{minipage}{0.45\textwidth}
\centering

        \includegraphics[width=0.85\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}

    \captionof{figure}{The two figures represent the predictions of the CNN on the CREMI dataset (\UPDATE{REF}) a) without added noise, b) with the addition of the merge-biased noise defined in Eq. \ref{eq:opensimplex_noise_def} and c) with split-biased noise. The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries \TODO{Add colorbar? Adapt to noise defs}}
    \label{fig:noisy_affs}
    \end{minipage}\hspace{0.04\textwidth}
\begin{minipage}{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
        \toprule
        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.343}  & 0.339  \\
GMIS \cite{liu2018affinity} & 0.341 & -  \\
Max &   0.243  &   0.325  \\
Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
Min &  0.000    & 0.000  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{AP scores on the cityscapes validation set for UGACA and different types of update rules. \TODO{PROBLEM: all apart from GMIS uses finetuned affinities} }
    \label{tab:results_cityscapes}
\end{minipage}
\end{minipage}
